A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex

\paragraph{Steinberg's Theorem} If the following inequalities hold
\begin{eqnarray}
	a_M &= \max_{1\leq i\leq n} a_i \\
	b_M &= \max_{1\leq i\leq n} b_i \\
\end{eqnarray}

>>>>

\paragraph{Steinberg's Theorem} Suppose that $w_M=\max_{1\leq i\leq n}w_i$, $h_M=\max_{1\leq i\leq n}h_i$, $a_i=w_ih_i$, and $A=\sum_{i=1}^{n}$. If the following inequalities hold,
\begin{equation}
	w_M\leq w, h_M\leq h, 2A\leq wh-(2w_M-w)_+(2h_M-h)+ 
	\label{cbase}
\end{equation}
then it is possible to pack the rectangles $R_1, R_2, \ldots, R_n$ into the bin $Q$ of size $w\times h$ by an efficient algorithm $M$\cite{steinberg1997strip}. The plus footnote returns the rectified linear value by $x_+=\max(x,0)$, which is a non-negative term.
\par Intuitively, inequalities \ref{cbase} states that the problem of packing the rectangles would be easy when the total area of $R_1$ to $R_n$ compared to the bin is not too big. This is consistent with our observation that when the bin is fairly large, simply sequentially packing rectangles would suffice.
\paragraph{Steinberg's algorithm for 2D packing} Based on the theorem, Steinberg gave a straight-forward algorithm to answer 2D packing problem. On input $R_1, R_2, \ldots, R_n$, the minimum $\hat{h}$ such that inequalities \ref{cbase} are satisfied with respect to bin $\hat{Q}$ of size $1\times \hat{h}$ is calculated as output. By substitution, the closed form representation of $\hat{h}$ is given by
\begin{equation}
	\hat{h}=\inf\{h:h_M\leq h \wedge 2A\leq h-(2w_M-1)_+(2h_M-h)_+\}
\end{equation}
It is easy to check that
\begin{equation}
	h=\max\{h_M, 2A+(2-\frac{1}{w_M})_+(h_M-A)\}
\end{equation}
which can be further relaxed to
\begin{equation}
	\hat{h}\leq A+\max(h_M, A)\leq OPT(L)+OPT(L)=2OPT(L)
\end{equation}
This gives an absolute performance bound of 2, which is a great improvement from the asymptotic performance bounds by former heuristic methods.
\paragraph{Recursive construction for $M$} Now we turn to the construction for the core algorithm $M$ for the correctness of the algorithm above.
